Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-26 paper/agree-semantics.tex
fixed bugs in Once/Since defs; added details to comparison with the INRIA work in Related Work
Add reference to PLTL monitor work by Hauvland and Rocu

The syntax of AGREE is
essentially that of quantifier-free first order predicate logic
supplemented with a few temporal operators. The terms (\emph{e}) are
arithmetic expressions built from variables ($v$) and numeric and
boolean literals ($c$), while formulas (\emph{b}) are built using
logical connectives from atomic formulas (\emph{a}) based on the
familiar comparison operators.
\[
\begin{array}{rcl}
e & ::= & v \mid c \mid e \;\set{+,*,/}\; e \\
a & ::= & e\; \set{=,<}\; e \\
b & ::= & v \mid c \mid a \mid \neg b
            \mid b \; \set{\land,\lor,\imp,\iff}\; b
\end{array}
\]
There is also a conditional, $\itelse{b}{(-)}{(-)}$, for both terms
and formulas. Lastly, there are temporal operators $\konst{pre}(-)$ (i.e., \emph{yesterday} in PLTL),
\emph{followed-by} $(-) \to (-)$, and $\konst{Hist}(-)$.

@@

Although basic, these definitions can be used to define higher-level
past-time operators from PLTL such as \konst{Once} and \konst{Since}.
These can be expressed in a recursive style as follows:
%% \[
%%    \begin{array}{rcl}
%%       \sem{\konst{Once}(b)}^E_t & = & \sem{b \vee (\konst{false} \to \konst{pre}(o))}^E_t \\
%%       \sem{\konst{Since}(a, b)}^E_t & = & \sem{b \vee (a and (\konst{false} \to \konst{pre}(o)))}^E_t \\
%%    \end{array}
%% \]
\[
\begin{array}{rcl}
 \konst{Once}(b) & = & b \vee \konst{pre}(\konst{Once}(b)) \\
 \konst{Since}(a, b) & = & b \lor (a \land \konst{pre}(\konst{Since}(a, b))
   \end{array}
\]

$\konst{Once}(b)$ is true if $b$ has ever been true before, or in, the
current moment.  $\konst{Since}(a, b)$ is true if $a$ has been true in
all moments up to the present one since $b$ most recently became true.
All other past-time operators of PLTL can be defined similarly.

>>>>

The syntax of AGREE is
essentially that of quantifier-free first order predicate logic
supplemented with a few temporal operators. The terms (\emph{e}) are
arithmetic expressions built from variables ($v$) and numeric and
boolean literals ($c$), while formulas (\emph{b}) are built using
logical connectives from atomic formulas (\emph{a}) based on the
familiar comparison operators.
\[
\begin{array}{rcl}
e & ::= & v \mid c \mid e \;\set{+,*,/}\; e \\
a & ::= & e\; \set{=,<}\; e \\
b & ::= & v \mid c \mid a \mid \neg b
            \mid b \; \set{\land,\lor,\imp,\iff}\; b
\end{array}
\]
There is also a conditional, $\itelse{b}{(-)}{(-)}$, for both terms
and formulas. Lastly, there are temporal operators \emph{previously} $\konst{pre}(-)$,
\emph{followed-by} $(-) \to (-)$, and historically $\konst{Hist}(-)$.
These temporal operators are sufficient to define all other past-time operators \cite{monitor}.

@@

Although basic, these definitions can be used to define higher-level
past-time operators from PLTL such as \konst{Once} and \konst{Since}.
These can be expressed in a recursive style as follows:
%% \[
%%    \begin{array}{rcl}
%%       \sem{\konst{Once}(b)}^E_t & = & \sem{b \vee (\konst{false} \to \konst{pre}(o))}^E_t \\
%%       \sem{\konst{Since}(a, b)}^E_t & = & \sem{b \vee (a and (\konst{false} \to \konst{pre}(o)))}^E_t \\
%%    \end{array}
%% \]
\[
\begin{array}{rcl}
\konst{Once}(b) & = & b \to b \vee \konst{pre}(\konst{Once}(b)) \\
\konst{Since}(a, b) & = & b \to b \lor (a \land \konst{pre}(\konst{Since}(a, b))
\end{array}
\]
\noindent $\konst{Once}(b)$ is true if $b$ has ever been true before, or in, the
current moment.  $\konst{Since}(a, b)$ is true if $a$ has been true in
all moments up to the present one since $b$ most recently became true.
All other past-time operators of PLTL can be defined similarly \cite{monitor}.
